### 2019-10-09 tim-lucas-model-ensembles.tex
Switch tables to sort by country then CV.

\begin{table}[h!]
\caption{Pearson correlations between observed and predicted values. }
\centering
\begin{tabular}{llrrrr}
Cross-validation scheme & Country &  Enviro &  ML\textsubscript{l} &  Enviro + ML\textsubscript{l} \\
\hline 
 Random &  Colombia & 0.59 & 0.59 & \textbf{0.61} \\
 Random &  Madagascar &  0.70 &  \textbf{0.73} & 0.69 \\
 Random &  Senegal &  \textbf{0.58} &  0.51 & 0.57 \\
 Random &  Indonesia &  0.52 &  0.48 &  \textbf{0.59} \\
 Spatial &  Colombia &  0.12 &  \textbf{0.33} &  0.25\\
 Spatial &  Madagascar &  0.22 &  \textbf{0.66} & 0.18\\
 Spatial &  Senegal &  \textbf{0.63} &  0.27 &  \textbf{0.63} \\
 Spatial &  Indonesia &  0.45 &  0.44 &  \textbf{0.51} \\
\end{tabular}
\label{t:results}
\end{table}

\begin{table}[h!]
\caption{Pearson correlations between observed and predicted values. }
\centering
\begin{tabular}{llrrrr}
Cross-validation scheme & Country &  Covariates &   ML\textsubscript{g} & ML\textsubscript{l} + ML\textsubscript{g} \\
\hline 
 Random &  Colombia & \textbf{0.59} &0.58 & 0.56 \\
 Random &  Madagascar &  0.70 &  0.70 & \textbf{0.71} \\
 Random &  Senegal &  \textbf{0.58} &  0.30 & 0.08 \\
 Random &  Indonesia &  \textbf{0.52} & 0.46 & 0.32 \\
 Spatial &  Colombia &  0.12 &  0.18 & \textbf{0.34}\\
 Spatial &  Madagascar &  0.22 &  \textbf{0.63} & 0.60\\
 Spatial &  Senegal &  \textbf{0.63} & 0.36 & 0.35 \\
 Spatial &  Indonesia &  \textbf{0.45} & 0.41 & \textbf{0.45} \\
\end{tabular}
\label{t:results}
\end{table}

>>>>

\begin{table}[h!]
\caption{Pearson correlations between observed and predicted values. }
\centering
\begin{tabular}{llrrrr}
Cross-validation scheme & Country &  Enviro &  ML\textsubscript{l} &  Enviro + ML\textsubscript{l} \\
\hline 
 Random &  Colombia & 0.59 & 0.59 & \textbf{0.61} \\
 Spatial &  Colombia &  0.12 &  \textbf{0.33} &  0.25\\
 Random &  Madagascar &  0.70 &  \textbf{0.73} & 0.69 \\
 Spatial &  Madagascar &  0.22 &  \textbf{0.66} & 0.18\\
 Random &  Senegal &  \textbf{0.58} &  0.51 & 0.57 \\
 Spatial &  Senegal &  \textbf{0.63} &  0.27 &  \textbf{0.63} \\
 Random &  Indonesia &  0.52 &  0.48 &  \textbf{0.59} \\
 Spatial &  Indonesia &  0.45 &  0.44 &  \textbf{0.51} \\
\end{tabular}
\label{t:results}
\end{table}

\begin{table}[h!]
\caption{Pearson correlations between observed and predicted values. }
\centering
\begin{tabular}{llrrrr}
Cross-validation scheme & Country &  Covariates &   ML\textsubscript{g} & ML\textsubscript{l} + ML\textsubscript{g} \\
\hline 
 Random &  Colombia & \textbf{0.59} &0.58 & 0.56 \\
 Spatial &  Colombia &  0.12 &  0.18 & \textbf{0.34}\\
 Random &  Madagascar &  0.70 &  0.70 & \textbf{0.71} \\
 Spatial &  Madagascar &  0.22 &  \textbf{0.63} & 0.60\\
 Random &  Senegal &  \textbf{0.58} &  0.30 & 0.08 \\
 Spatial &  Senegal &  \textbf{0.63} & 0.36 & 0.35 \\
 Random &  Indonesia &  \textbf{0.52} & 0.46 & 0.32 \\
 Spatial &  Indonesia &  \textbf{0.45} & 0.41 & \textbf{0.45} \\
\end{tabular}
\label{t:results}
\end{table}
